Assignment 1 - Starting with R and TraMineR
===========================================
**Start R and load the TraMineR library**

```{r library, message=FALSE}
# Load the TraMineR library
library(TraMineR)
```

**Look at the help page of the biofam data provided by TraMineR which you access by typing help(biofam) or ?biofam**
Find out which are the columns containing the sequence data

```{r data, message=FALSE}
# Get help for biofam data set
help(biofam)
# Load the biofam data
data(biofam)
```

**Look at the first six rows of the data frame (head(biofam))**

```{r header}
# biofam data header
head(biofam)
```


**Create the state sequence object**

```{r seqobj, message=FALSE}
# Create labels for biofam alphabet
biofam.lab <- c("Parent","Left","Married","Left+Marr","Child","Left+Child","Left+Marr+Child","Divorced")
# Create biofam state sequence object
biofam.seq<-seqdef(biofam,10:25,states=biofam.lab)
```

**plot the sequences using, seqIplot, seqfplot and seqdplot. Comment the plots**

```{r plots}
# Generate sequence index plot
seqIplot(biofam.seq,title="Index plot (whole biofam dataset)",sortv="from.start")
# Generate sequence frequency plot
seqfplot(biofam.seq,title="Frequency plot (10 most frequent sequences)")
# Generate state distribution plot
seqdplot(biofam.seq,title="State distribution plot",border=NA)
```

**Display (print) the first 10 sequences in extended and compact form**

```{r print,}
# First 10 sequences in extended form
print(biofam.seq[1:10,],ext=T)
# First 10 sequences in compact form
print(biofam.seq[1:10,],format="SPS")
```
